Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-23 WSSSPE3/report/WSSSPE3_review.tex
small edits in conclusion notes

\todo{need to update for WSSSPE3}
The WSSSPE3 workshop continued our experiment from WSSSPE1 and WSSSPE2 in how we can
collaboratively build a workshop agenda, and we began a new experiment in
how to build a series of workshops into an ongoing community activity.

The differences in workshop organization in WSSSPE2 from WSSSPE1
are in using an existing service (EasyChair) to handle submissions and reviews,
rather than an ad hoc process, and using an existing service (Well Sorted) to
allow collaborative grouping of papers into themes by all authors, reviewers,
and the community, rather than this being done in an ad hoc manner by the
organizers alone.

@@

\begin{table*}[t]
\centering
\caption{Top tweets tagged \#WSSSPE or \#WSSSPE3 on Sep.\ 28--29, 2015. \todo{update this for WSSSPE3?}}\label{tab:tweets}
  \begin{scriptsize}
  \begin{tabular}{@{}l l l l@{}}
 \toprule
    Author  &   Tweet  & Retweets &  Favorites
\\ \midrule
Neil P Chue Hong  &  Getting ready for the start of the \#WSSSPE workshop & 2 & 1
\\ & \url{http://wssspe.researchcomputing.org.uk/wssspe3/agenda/}  & &
\\ & Video stream: \url{http://ucarconnect.ucar.edu/live?room=cg1aud} & &
%
\\ August Muench & Astronomy \& Software for a totally distracting Monday (2/2) => & 1 & 3
\\ & Workshop on Sustainable SW for Science \#WSSSPE3 & & 
\\ & \url{http://wssspe.researchcomputing.org.uk/wssspe3/agenda/} & &
%
\\ Neil P Chue Hong & My \#WSSSPE lightning talk on Building a Scientific Software & 6 & 3
\\ &  Accreditation Framework: \url{http://dx.doi.org/10.6084/m9.figshare.1555925} & & 
%
\\ Mozilla Science Lab & At \#wssspe3 and want to learn more about our Working Open guide & 2 & 1 
\\ &  or Contributorship badges pilot? Keep an eye out for @abbycabs! & & 
%
\\ Daniel S.\ Katz & \#wssspe starting! & 1 & 3
%
\\ Daniel S.\ Katz & @powersoffour starting \#wssspe keynote & 1 & 2
%
\\ Neil P Chue Hong   &  The difference between software presented at SC \& SciPy & 1 & 4
\\  &  according to @powersoffour straw person \#wssspe & &
%
\\ Daniel S.\ Katz & sustainability may mean: keeps up with bug reports, adds new features, & 3 & 1
\\ &  works on new architectures (1/2)  -- @powersoffour at \#wssspe (1/2) & & 
%
\\ Daniel S.\ Katz & sustainability may mean: people use it, keeps getting funded, produces & 2 & 
\\ &  same results, transits over people (2/2)  -- @powersoffour at \#wssspe & &
%
\\ Nic Weber & Rec, by Matt Turk: Ash Dryden - Ethics of Unpaid Labor & 3 & 2 
\\ & \url{http://t.co/KfMwS4VG4N} & &
%
\\ Nic Weber & My .02 - many more models (than 3) for sustaining sci. software. & 3 & 2
\\ & See this pub on open-source:  & & 
\\ & \url{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2568185} & &
%
\\ Erin Robinson & \#WSSSPE - Software is like a vampire. It's only dead if you really kill it. & 2 & 2
%
\\ Neil P Chue Hong & Absolutely great \#wssspe keynote from @powersoffour to inspire & 2 & 1 
\\ & the workshop. Should be archived via & & 
\\ & \url{http://ucarconnect.ucar.edu/live?room=cg1aud#.VgmpvCdIrCQ} soon & & 
%
\\ Daniel S.\ Katz & \#wssspe lightning talks starting - streaming at  & 5  &  1
\\ &  \url{http://ucarconnect.ucar.edu/live?room=cg1aud} & & 
%
\\ Kyle Niemeyer & Participatory open source means better documentation  & 2 & 1 
\\ & (readme, roadmap, contributing) ? @abbycabs at \#wssspe & &
%
\\ Erin Robinson & Interesting resource: \url{http://mozillascience.github.io/leadership-training/} & 2 & 
\\ &  \#WSSSPE cc: @abbycabs & & 
%
\\ Nic Weber & @MozillaScience + @abbycabs giving look at cool resources & 2 & 3
\\ & for leading an open source community & & 
\\ & \url{http://mozillascience.github.io/leadership-training/} & & 
%
\\ Nic Weber & Some interesting sepeartion of best practices for Geosoftware dev & 2 & 
\\ & into categories \url{https://geodynamics.org/cig/dev/best-practices} & &
%
\\ Neil P Chue Hong & Some statistics of software citation in geodynamics & 2 & 
%
\\ Daniel S.\ Katz & @jamespjh goal: make research software less rubbish; solution is RSEs & 3 & 
%
\\ Nic Weber & Highly relevant to \#wssspe crowd - @Impactstory team is launching & 7 & 3
\\ & a impact of research software project \url{http://depsy.org/}  \#verycool & & 
%
\\ Neil P Chue Hong & @jamespjh talking about Research Software Engineer groups in the UK & 2 & 1
\\ &  \#wssspe @ResearchSoftEng @SoftwareSaved & & 
%
\\ Abby Cabunoc Mayes & Wonderful time @ \#WSSSPE 3! Encouraging 2 see a diverse community & 1 & 2 
\\ & working 2gether (\& making real plans!) \url{http://gif.co/s6v4.gif} & & 
%
\\ \bottomrule
    \end{tabular}
    \end{scriptsize}
\end{table*}

>>>>

The WSSSPE3 workshop continued our experiment from WSSSPE1 and WSSSPE2 in how we can
collaboratively build a workshop agenda, and we began a new experiment in
how to build a series of workshops into an ongoing community activity.

\todo{need to update rest of this section for WSSSPE3, except the tweet table has already been updated}
The differences in workshop organization in WSSSPE2 from WSSSPE1
are in using an existing service (EasyChair) to handle submissions and reviews,
rather than an ad hoc process, and using an existing service (Well Sorted) to
allow collaborative grouping of papers into themes by all authors, reviewers,
and the community, rather than this being done in an ad hoc manner by the
organizers alone.

@@

\begin{table*}[t]
\centering
\caption{Top tweets tagged \#WSSSPE or \#WSSSPE3 on Sep.\ 28--29, 2015.}\label{tab:tweets}
  \begin{scriptsize}
  \begin{tabular}{@{}l l l l@{}}
 \toprule
    Author  &   Tweet  & Retweets &  Favorites
\\ \midrule
Neil P Chue Hong  &  Getting ready for the start of the \#WSSSPE workshop & 2 & 1
\\ & \url{http://wssspe.researchcomputing.org.uk/wssspe3/agenda/}  & &
\\ & Video stream: \url{http://ucarconnect.ucar.edu/live?room=cg1aud} & &
%
\\ August Muench & Astronomy \& Software for a totally distracting Monday (2/2) => & 1 & 3
\\ & Workshop on Sustainable SW for Science \#WSSSPE3 & & 
\\ & \url{http://wssspe.researchcomputing.org.uk/wssspe3/agenda/} & &
%
\\ Neil P Chue Hong & My \#WSSSPE lightning talk on Building a Scientific Software & 6 & 3
\\ &  Accreditation Framework: \url{http://dx.doi.org/10.6084/m9.figshare.1555925} & & 
%
\\ Mozilla Science Lab & At \#wssspe3 and want to learn more about our Working Open guide & 2 & 1 
\\ &  or Contributorship badges pilot? Keep an eye out for @abbycabs! & & 
%
\\ Daniel S.\ Katz & \#wssspe starting! & 1 & 3
%
\\ Daniel S.\ Katz & @powersoffour starting \#wssspe keynote & 1 & 2
%
\\ Neil P Chue Hong   &  The difference between software presented at SC \& SciPy & 1 & 4
\\  &  according to @powersoffour straw person \#wssspe & &
%
\\ Daniel S.\ Katz & sustainability may mean: keeps up with bug reports, adds new features, & 3 & 1
\\ &  works on new architectures (1/2)  -- @powersoffour at \#wssspe (1/2) & & 
%
\\ Daniel S.\ Katz & sustainability may mean: people use it, keeps getting funded, produces & 2 & 
\\ &  same results, transits over people (2/2)  -- @powersoffour at \#wssspe & &
%
\\ Nic Weber & Rec, by Matt Turk: Ash Dryden - Ethics of Unpaid Labor & 3 & 2 
\\ & \url{http://t.co/KfMwS4VG4N} & &
%
\\ Nic Weber & My .02 - many more models (than 3) for sustaining sci. software. & 3 & 2
\\ & See this pub on open-source:  & & 
\\ & \url{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2568185} & &
%
\\ Erin Robinson & \#WSSSPE - Software is like a vampire. It's only dead if you really kill it. & 2 & 2
%
\\ Neil P Chue Hong & Absolutely great \#wssspe keynote from @powersoffour to inspire & 2 & 1 
\\ & the workshop. Should be archived via & & 
\\ & \url{http://ucarconnect.ucar.edu/live?room=cg1aud#.VgmpvCdIrCQ} soon & & 
%
\\ Daniel S.\ Katz & \#wssspe lightning talks starting - streaming at  & 5  &  1
\\ &  \url{http://ucarconnect.ucar.edu/live?room=cg1aud} & & 
%
\\ Kyle Niemeyer & Participatory open source means better documentation  & 2 & 1 
\\ & (readme, roadmap, contributing) ? @abbycabs at \#wssspe & &
%
\\ Erin Robinson & Interesting resource: \url{http://mozillascience.github.io/leadership-training/} & 2 & 
\\ &  \#WSSSPE cc: @abbycabs & & 
%
\\ Nic Weber & @MozillaScience + @abbycabs giving look at cool resources & 2 & 3
\\ & for leading an open source community & & 
\\ & \url{http://mozillascience.github.io/leadership-training/} & & 
%
\\ Nic Weber & Some interesting sepeartion of best practices for Geosoftware dev & 2 & 
\\ & into categories \url{https://geodynamics.org/cig/dev/best-practices} & &
%
\\ Neil P Chue Hong & Some statistics of software citation in geodynamics & 2 & 
%
\\ Daniel S.\ Katz & @jamespjh goal: make research software less rubbish; solution is RSEs & 3 & 
%
\\ Nic Weber & Highly relevant to \#wssspe crowd - @Impactstory team is launching & 7 & 3
\\ & a impact of research software project \url{http://depsy.org/}  \#verycool & & 
%
\\ Neil P Chue Hong & @jamespjh talking about Research Software Engineer groups in the UK & 2 & 1
\\ &  \#wssspe @ResearchSoftEng @SoftwareSaved & & 
%
\\ Abby Cabunoc Mayes & Wonderful time @ \#WSSSPE 3! Encouraging 2 see a diverse community & 1 & 2 
\\ & working 2gether (\& making real plans!) \url{http://gif.co/s6v4.gif} & & 
%
\\ \bottomrule
    \end{tabular}
    \end{scriptsize}
\end{table*}
